Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2022-01-25 edubots_surveys.Rnw
Fixed format problems

The \bf{second survey} was designed after initial results to the first survey arrived,
and pointed to necessities and experiences of teachers not being addressed by the first one; namely
their experience with messaging platforms and the way they were used to interact with students.
It was piloted in a group of university teachers attending to a formation course, and validated with them.
It was then extended to the rest of the responders, using the same media: Telegram groups, email and announcement in mailing lists. The questions asked in that survey are also shown in Appendix I
(Section \ref{app:questions}).

@@

One of the questions we made in the \bf{second survey}, related to
the messaging applications used by tertiary education teachers, opens a new line
of inquiry about what they {\em perceive} as such, and about how it is used.
Namely, the responses indicated that the teachers perceived as messaging
application not only what is usually called a chat or instant messaging app such
as WhatsApp or Microsoft Teams, but also the means provided by the university for
communicating with the student, such as a feature of grading applications that
will email the grade to the student. This implies that there is a need by
teachers, communication with students, also mostly unidirectional, and that it
does not matter so much how that need is covered. However, this will need careful
consideration, including how it ties with the automation of the learning
experience that the chatbots bring.

>>>>

The {\bf second survey} was designed after initial results to the first survey arrived,
and pointed to necessities and experiences of teachers not being addressed by the first one; namely
their experience with messaging platforms and the way they were used to interact with students.
It was piloted in a group of university teachers attending to a formation course, and validated with them.
It was then extended to the rest of the responders, using the same media: Telegram groups, email and announcement in mailing lists. The questions asked in that survey are also shown in Appendix I
(Section \ref{app:questions}).

@@

One of the questions we made in the {\bf second survey}, related to
the messaging applications used by tertiary education teachers, opens a new line
of inquiry about what they {\em perceive} as such, and about how it is used.
Namely, the responses indicated that the teachers perceived as messaging
application not only what is usually called a chat or instant messaging app such
as WhatsApp or Microsoft Teams, but also the means provided by the university for
communicating with the student, such as a feature of grading applications that
will email the grade to the student. This implies that there is a need by
teachers, communication with students, also mostly unidirectional, and that it
does not matter so much how that need is covered. However, this will need careful
consideration, including how it ties with the automation of the learning
experience that the chatbots bring.
